Software Ticket Quality

### 2017-11-26 proposal/mprop.tex
Complete study design

Last but not least, we did a literature review on sentiment analysis as well because
we will inspect, among other components of a ticket, comments - we want to analyze
the textual representation of comments and see if the overall sentiment might influence
the time it takes to close a ticket (i.e. maybe a negative conversation in comments 
might increase the time it takes to solve the issue).

@@

What was covered and why; How papers were found; what terms were searched 
for + snowballing.

>>>>

Last but not least, we did a literature review on sentiment analysis as well because
we will inspect, among other components of a ticket, comments - we want to analyze
the textual representation of comments and see if the overall sentiment influences
the time it takes to close a ticket (i.e. maybe a negative conversation in comments 
might increase the time it takes to solve the issue).

@@
